How to Schedule Periodic Messages in a Network Without Congestion

### 2017-06-05 article/article.tex
lundi aprem quelques typos

      A {\bf $(P,\tau)$-periodic assignment} of a routage graph $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$. The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$. We will always consider that the $m_{i}$ are between $O$ and $P-1$. A $(P,\tau)$-periodic assignment must have no {\bf collision} between two routes in $\cal R$, that is $\forall (r_{i}, r_{j}) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$, 
      we have $$[t(u,r_{i})] \cap [t(u,r_{j})] = \emptyset .$$

%       Notice that the notion of $P$-periodic assignment \textbf{is not monotone} with regard to $P$. 
      As an example of a $(2,1)$-periodic assignment, let consider a routage graph with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
      We set $\tau = 1$ and the delays are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.

@@

  We propose two algorithms that always find a solution in polynomial time if the instance meets some criteria (short routes or great enough period) but which may fail in other cases and one exponential algorithm which always finds a solution if it exists.

>>>>

      A {\bf $(P,\tau)$-periodic assignment} of a routage graph $(G,\cal R)$ is a sequence  ${\cal M}=(m_1, \ldots ,m_n)$ of $n$ integers that we call {\bf offsets}, with $n$ the number of routes in $\cal R$. The number $m_{i}$ represents the time at which a message is emitted at the first vertex of the route $r_{i}$. We will always consider that the $m_{i}$ are between $0$ and $P-1$. A $(P,\tau)$-periodic assignment must have no {\bf collision} between two routes in $\cal R$, that is $\forall (r_{i}, r_{j}) \in {\cal R}^2, i \neq j$, % with $\tau$ the size (in number of consecutive slots) of each message that must be periodically sent on each route of ${\cal R}_{\cal C}$, 
      we have $$[t(u,r_{i})] \cap [t(u,r_{j})] = \emptyset .$$

%       Notice that the notion of $P$-periodic assignment \textbf{is not monotone} with regard to $P$. 
      As an example of a $(2,1)$-periodic assignment, let us consider a routage graph with routes $\{r_{i}\}_{i=1,\dots,n}$, such that all pairs of routes intersect at a different edge.
      We set $\tau = 1$ and the delays are chosen so that if $r_{i}$ and $r_{j}$ have $v$ as first common vertex then we have $\lambda(v,r_{i}) - \lambda(v,r_{j})=1$.There is a $(2,1)$-periodic assignment by setting all $m_{i}$ to $0$.

@@

  We propose two algorithms that always find a solution in polynomial time if the instances meets some criteria (short routes or great enough period) but which may fail in other cases and one exponential algorithm which always finds a solution if it exists.
